---
title: "Weight of Fish"
author: "Deniss Gonzalez Ramirez"
date: "November 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```


```{r}
Fish=read.csv("Fish.csv")
```



# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  

# Perch
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I will be getting a subset of fish that contains the species that I would like to analyze and then I will look at how well each combination of the predictor variables can predict the weight of the fish. I will be using the perch subset in my analysis.

```{r}
Perch=filter(Fish,Species=="Perch")
```



# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
basicNN <- ggplot(Perch,aes(y=Weight,x=Length1))
```
## Now add in scatterplot

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 



### Numerical Descriptive Results  

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select(Perch,-Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


## Which model is best?

The best model is that which utilizes two variables, Height and Width.


```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
best.model <- lm(Weight ~ Height + Width,data = Perch)
summary(best.model)
fullup=lm(Weight~.,data= select (Perch, - Species))
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$: There is no difference between models 1 and 2 when predicting the weight of the fish (Perch)

$H_A$: There is a difference between models 1 and 2 when predicting the weight of the fish ( Perch)


```{r}
anova(fullup,best.model)
```

We fail to reject the null hypothesis because the p-value is high at 0.879


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Based on the automated selection of the variables there is a difference in using a model with two variables verses using one with all of the variables. This was identified through a graphical depiction of the adjusted R-squared value and the p-value. In the case of Roach, we fail to reject the null hypothesis because the p-value associated with the anovas is high at 0.879.  

# Pike
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I will be getting a subset of fish that contains the species that I would like to analyze and then I will look at how well each combination of the predictor variables can predict the weight of the fish. I will be using the Pike subset in my analysis.

```{r}
Pike=filter(Fish,Species=="Pike")
```



# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
basicNN <- ggplot(Pike,aes(y=Weight,x=Length1))
```
## Now add in scatterplot

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 



### Numerical Descriptive Results  

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select(Pike,-Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


## Which model is best?

In the case of Pike, the best model is the model with three variables, Length1 Length 3 and Width, however the best two variable model is Length 1 and Length 3.


```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
best.model <- lm(Weight ~ Length1 + Length3,data = Pike)
summary(best.model)
fullup=lm(Weight~.,data= select (Pike, - Species))
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$: There is no difference between models 1 and 2 when predicting the weight of the fish (Pike)

$H_A$: There is a difference between models 1 and 2 when predicting the weight of the fish ( Pike)


```{r}
anova(fullup,best.model)
```
According to the anova, we have to reject the null hypothesis because the p-value is low at 0.03091.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Based on the automated selection of the variables there is a difference in using a model with two variables verses using one with all of the variables. This was identified through a graphical depiction of the adjusted R-squared value and the p-value. According to the anova, we have to reject the null hypothesis because the p-value is low at 0.03091. In terms of Pike fish, there is a difference in which models are better at predicting the weight of the fish.


# Roach
# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I will be getting a subset of fish that contains the species that I would like to analyze and then I will look at how well each combination of the predictor variables can predict the weight of the fish. I will be using the Roach subset in my analysis.

```{r}
Roach=filter(Fish,Species=="Roach")
```



# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
basicNN <- ggplot(Roach,aes(y=Weight,x=Length1))
```

## Now add in scatterplot

```{r}
basicNN + geom_point()
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 



### Numerical Descriptive Results  

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = select(Roach,-Species),
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

## Which model is best?

In the case of Roach, the best model is the model with Length 3 and Width.

```{r}
which.max(summary.out$adjr2)
```
```{r}
summary.out$which[2,]
```
```{r}
best.model <- lm(Weight ~ Length3 + Width,data=Roach)
summary(best.model)
fullup=lm(Weight~.,data= select (Roach, - Species))
```


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

$H_0$: There is no difference between models 1 and 2 when predicting the weight of the fish (Roach)

$H_A$: There is a difference between models 1 and 2 when predicting the weight of the fish (Roach)


```{r}
anova(fullup,best.model)
```

We fail to reject the null hypothesis because the p-value is high at 0.9338 based on the anova test above.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


Based on the automated selection of the variables there is a difference in using a model with two variables verses using one with all of the variables. This was identified through a graphical depiction of the adjusted R-squared value and the p-value. In the case of Roach, we fail to reject the null hypothesis because the p-value associated with the anovas is high at 0.9338.  